---
title: "A-quick-tour-of-STMoE"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-quick-tour-of-STMoE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
	fig.align = "center",
	fig.height = 5.5,
	fig.width = 6,
	warning = FALSE,
	collapse = TRUE,
	dev.args = list(pointsize = 10),
	out.width = "90%",
	par = TRUE
)
knit_hooks$set(par = function(before, options, envir)
  { if (before && options$fig.show != "none") 
       par(family = "sans", mar = c(4.1,4.1,1.1,1.1), mgp = c(3,1,0), tcl = -0.5)
})
```

```{r, message = FALSE, echo = FALSE}
library(STMoE)
```

# Introduction

**STMoE** is a contributed R package for segmentation. It provides functions for parameter estimation via the EM algorithm. This document gives a quick tour of **STMoE** (version `r packageVersion("STMoE")`) functionalities. It was written in R Markdown, using the [knitr](https://cran.r-project.org/package=knitr) package for production. 
See `help(package="STMoE")` for further details and references provided by `citation("STMoE")`.

# Load data

```{r}
data("simulatedstructureddata")
fData <- FData$new()
fData$setData(simulatedstructureddata$X, simulatedstructureddata$Y)
```

# Set up STMoE model parameters

```{r}
K <- 2 # number of regimes (mixture components)
p <- 1 # dimension of beta (order of the polynomial regressors)
q <- 1 # dimension of w (order of the logistic regression: to be set to 1 for segmentation)

modelSTMoE <- ModelSTMoE(fData, K, p, q)
```

# Set up EM parameters

```{r}
n_tries <- 1
max_iter = 1500
threshold <- 1e-5
verbose <- TRUE
verbose_IRLS <- FALSE
```

# Estimation

```{r}
solution <- EM(modelSTMoE, n_tries, max_iter, threshold, verbose, verbose_IRLS)
```


# Plots

```{r}
solution$plot()
```
